# Introduction {#intro}

**#Data Visualization** 
Data visualization refers to representing data in a visual context to help people understand the significance of that data. A way so that information, numbers, and measurements makes sense is a form of art – the art of data visualization. Graphs do that for us.

Plot links:
https://datavizcatalogue.com/search.html

https://infogram.com/page/data-visualization


You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).
https://eagereyes.org/
https://research.tableau.com/user/robert-kosara
https://twitter.com/eagereyes?ref_src=twsrc%5Egoogle%7Ctwcamp%5Eserp%7Ctwgr%5Eauthor
http://flowingdata.com/
https://data-visualization.cioreview.com/cxoinsight/what-is-data-visualization-and-why-is-it-important-nid-11806-cid-163.html
  
  
About David McCandless’s TED talk on data visualization: https://www.ted.com/talks/david_mccandless_the_beauty_of_data_visualization

Visuals help us understand concepts that would otherwise be difficult to contextualize—for example, expenditures or valuations of extremely large amounts of money are represented in the billion dollar-o-gram by color-coded, relatively-sized boxes.  Furthermore, it allows synthesis of a breadth of information to be delivered in a small, easily-digestible, aesthetically pleasing way.  Visuals serve as a sort of map for a vast landscape of information—they direct your eyes to the important places and details.  And the eye, as McCandless notes, is uniquely suited among our senses to process large amounts of information and detect patterns.  

The billion dollar-o-gram is extremely readable and rather pretty, but it seems a bit dubious to compare the predicted Iraq War cost to the “mushroomed” actual cost of Iraq and Afghanistan wars, since its purpose seems only to conflate two wars for dramatic effect.  

Beyond its ability to make information from several different sources and in large amounts more quickly and easily understood, data visualization can also reveal smaller interesting patterns—allowing us to play the “data detective” as McCandless calls it.  In other words, as we have already discussed, data visualization can not only be extremely effective in a declarative manner, but can also be used as an exploratory tool.    

McCandless also postulates that we all have a latent “design literacy” that is being developed every day as we are constantly bombarded with visuals, and that our minds and our eyes are taking in this information and processing it so that we all have an intuitive sense of design, and have actually begun to demand a visual aspect to our information.  This is an interesting perspective, since everyone does seem to have a sense of visual aspects—space, color, etc., but of course the time-honored adage tells us that beauty is in the eye of the beholder.  So while it might be whimsical to claim that we are all designers, there is still, of course, great value in learning formal principles of design.  


Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
