# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).
https://eagereyes.org/
https://research.tableau.com/user/robert-kosara
https://twitter.com/eagereyes?ref_src=twsrc%5Egoogle%7Ctwcamp%5Eserp%7Ctwgr%5Eauthor
http://flowingdata.com/
https://data-visualization.cioreview.com/cxoinsight/what-is-data-visualization-and-why-is-it-important-nid-11806-cid-163.html

The article , written by Chris Pittenturf, VP-Data & Analytics, Palace Sports & Entertainment, talks about what data visualization is and its importance to the businesses today.
The article begins with a definition of data visualization in simple terms and goes on to explain how a good data visualization should be visually engaging to the reader. Chris goes on to explain the basic criterias that a data visualization should satisfy to be an effective visualization. These criterias and their brief meanings are as follows:
1.	Informative: The visualization should be able to convey the information of the data to the reader
2.	Efficient: The visualization should not be ambiguous.
3.	Appealing: The visualization should be captivating and visually pleasing. 
4.	(Optional) Interactive and Predictive: The visualizations can contain variables and filters for the users to interact with the visualizations in order to predict results of different scenarios.

Chris goes on to give various day-to-day examples where visualization gives a better understanding of the data.
One extremely simple example used by Chris is that of an energy bill. Chris states that as a consumer, when we receive an energy bill, we normally look at the graph in the bill first before proceeding to read the text in the bill. Chris states that consumers are more likely to analyze and understand the visualizations before reading further along. 
The article ends with Chris emphasizing the importance of data visualizations in our businesses as well as in our daily lives.
According to me, the article gives a simple, short and crisp understanding of what data visualization is and how it is relevant to everyone. It shows that data visualization is an aid to get a better understanding of the complex insights that any business data provides. Most of the data used by the businesses is highly unstructured and these businesses can get a better understanding of their businesses by visualizing their data.

  
Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
