# Introduction {#intro}

[Minard's Version of Napoleons March](https://en.wikipedia.org/wiki/Charles_Joseph_Minard#/media/File:Minard.png)

**#Data Visualization** 
Data visualization refers to representing data in a visual context to help people understand the significance of that data. A way so that information, numbers, and measurements makes sense is a form of art – the art of data visualization. Graphs do that for us.

Plot links:
https://datavizcatalogue.com/search.html

https://infogram.com/page/data-visualization


You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).
https://eagereyes.org/
https://research.tableau.com/user/robert-kosara
https://twitter.com/eagereyes?ref_src=twsrc%5Egoogle%7Ctwcamp%5Eserp%7Ctwgr%5Eauthor
http://flowingdata.com/
https://data-visualization.cioreview.com/cxoinsight/what-is-data-visualization-and-why-is-it-important-nid-11806-cid-163.html
  
Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
